---
params:
  kapitel_name: "TEST" 
  kapitel_nr: 6 

title: "`r params$kapitel_name`"
subtitle: "`r  paste0('Kapitel ', params$kapitel_nr)`"
#date: WiSe 21

#institute: AWM, HS Ansbach
output:
  xaringan::moon_reader:
    keep_md: false
    css: ["footer-header.css", "my-css.css","xaringan-themer.css",  "hygge", "default-fonts"]
    lib_dir: libs
    seal: true
    nature:
      titleSlideClass: ["right", "bottom", "test"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false

---




```{r QM2-Thema4-Gaussmodelle-1, child="children/Setup.Rmd"}
```


```{r}
book <- "Rethink, Kap. 4.4, ROS, Kap. 9.2"
```


---

name: gliederung
class: center, middle

## Gliederung



.xxlarge[
1. [Teil 1: Die Post-Verteilung der Regression berechnen](#teil-1)

2. [Teil 2: Die Post-Verteilung befragen](#teil-2)

3. [Teil 3: Die PPV befragen](#teil-3)

4. [Hinweise](#hinweise)
]

---

## Box


.content-box-blue[asdjlö]
.bg-lightest-blue.b--blue.ba.bw2.br3.shadow-5.ph4.mt5[
The only way to write good code is to write tons of bad code first. 
Feeling shame about bad code stops you from getting to good code
]


$\newcommand{\indep}{\perp \!\!\! \perp}$




asdfjk

$X \indep Y$

---

## Ref tets

`r RefManageR::Citep(bib, "gelman_regression_2021")`


---

---


```{r QM2-Thema4-Gaussmodelle-1, child="children/Hinweise.Rmd"}
```

